Characteristics of Top Songs Has Changed from Pandemic Brain

### 2024-04-01 paper/paper.qmd
Updated paper.qmd's causal model size

1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; 6) why it is important; 7) the structure of the paper.

@@

# NOTE: Had to save diagram and read it in as a image since grViz can be only render in HTML and 
# not in PDFs 
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("casual_model.png")
plot.new()
rasterImage(the_image, 0, 0, 1, 1)
```

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

>>>>

@@

# NOTE: Had to save diagram and read it in as a image since grViz can be only render in HTML and 
# not in PDFs 
# Referenced https://stackoverflow.com/questions/23861000/displaying-images-in-r-in-version-3-1-0
the_image <- readPNG("casual_model.png")
plot.new()
rasterImage(the_image, 0, 0, 0.7, 1)
```

@@

We run the model in R [@citeR] using the `rstanarm` package of @citerstanarm. We use the default priors from `rstanarm`.
